\chapter{Lenses}
\label{chap:Lenses}

\input{Lenses/General-Introduction}

\input{Lenses/Types}

\section{What Lens should I buy?}

If you ask this question like this, without any context, I suggest you read section \ref{sec:Introduction-Types-Lenses} again. Choosing a lens is such an individual task, that nobody can give you the ``right'' answer.
\\
\\
If you are starting out, the kit lens on a \gls{DSLR} is a good starting point. A reasonably priced tele-zoom can be an idea, but is not a must have. From the kit lens you need to decide if your interest requires a wider angle or a tele-lens and then choose the appropriate lens.
\\
Alternatively, if you have an exact idea what you want to shoot, you can ask for a recommendation for this specific task, but keep in mind, that sometimes different people take different approaches to the same task.
\\
\\
Once you have decided which \gls{focallength} you aim to buy, the next point of concern would be the \gls{aperture}, as often multiple lenses with different \glspl{aperture} but the same \gls{focallength} are available. Well, this latter part is easy. The wider the \gls{aperture}, the heavier and also more expensive the lens. Consider the widest \gls{aperture} you can afford or are willing to afford and are willing to carry on any lens and research it. Unless you can find any specific issues with the model you researched, it will always have superior glass compared to the smaller \gls{aperture} model of the same \gls{focallength}.
\\
This does become a bit trickier, if your choice is between a lens with \gls{IS} or without, and the question you need to ask yourself is, how important is \gls{IS} to you. Keep in mind though, that a lack of \gls{IS} can be compensated for by a tripod in most situations, while a wider \gls{aperture} would require significant postprocessing work if it can be realistically simulated at all.
\\
At the same time, obviously, if you need a lens ``now'' and cannot afford say a 50mm f1.2 lens, a f1.4 or f1.8 will be a good choice, though they are optically inferior.
\\
Lastly, sometimes across different manufacturers, \glspl{focallength} vary slightly, by which I mean that competing lenses do not have identical \glspl{focallength}. Expect competing lenses between manufacturers to show a difference of 1 to 3mm on the wide end, and even up to 5mm on the long end.
